Peering Through Censorship:\\Tackling Internet Censorship Using P2P Networking

### 2023-02-02 paper.tex
Updates

The bedrock of the theory underlying succesful provision of access to proxies is collateral damage. We begin with a basic model - an adversary will engage in the censorship of service $x$ if $b_x - c_x > 0$, where $b_x$ is the benefit of engaging in censorship of service $x$ and $c_x$ is the cost of engaging in censorship of service $x$. We will refine this formula by switching to a focus on censorship techniques - $(b_x1 + b_x2 + ... + b_xn) - c_x > 0$, where $b_xn$ is the benefit of censoring service $n$ using method $x$, and $c_x$ is the cost of engaging in censorship method $x$. A censor will engage in any censorhip method where the benefit reaped by censoring \emph{any} desired services using that mathod is greater than 0.

We now note that each method may only stop a fraction of users accessing a service using a method - so a more realistic formulation would be $(u_x1*b_x1 + u_x1*b_x2 + ... + u_xn*b_xn) - c_x > 0$, where $u_xn$ is the fraction of users accessing a service are blocked from accessing service $n$ using method $x$.

We will now break down cost further. $c_x = f_x + m_x$ - where $f_x$ is the fixed cost of setting up method $x$ and $m_x$ is the marginal cost of actively engaging in $x$. We will drop $f_x$ from further consideration - the cost of setting up a method is a one time cost, and to an adversary with unlimited resources, expending a one time cost costs $0$ over the long run. We will now explore the marginal cost of $x$. Censorship

>>>>

The bedrock of the theory underlying succesful provision of access to proxies is collateral damage. We begin with a basic model - an adversary will engage in the censorship of service $x$ if $B_x - C_x > 0$, where $B_x$ is the average benefit per user of engaging in censorship of service $x$ and $C_x$ is the average cost of engaging in censorship of service $x$. We will refine this formula by switching to a focus on censorship techniques - $(b_{x,1} + b_{x,2} + ... + b_{x,n}) - C_x > 0$, where $b_{x,n}$ is the average benefit per user of censoring service $n$ using method $x$. A censor will engage in any censorhip method where the average benefit reaped by censoring \emph{any} desired services using that method is greater than the cost. Also note that these benefits and costs are based on how they are \emph{perceived} by the censor, not by an objective, bird-eye view of good vs. bad, and they may account for a variety of benefits/cost, including direct financial costs, but also including less tangible value such as "stability".

We now note that each method may only stop a fraction of users accessing a service using a method - so a more realistic formulation would be $(u_{x,1}*b_{x,1} + u_{x,2}*b_{x,2} + ... + u_{x,n}*b_{x,n}) - C_x > 0$, where $u_{x,n}$ is the fraction of users accessing service $n$ are blocked from accessing service $n$ using method $x$.

We will now break down cost further. $C_x = f_x + m_x$ - where $f_x$ is the fixed cost per user of setting up method $x$ and $m_x$ is the marginal cost of actively engaging in $x$ per user. We will drop $f_x$ from further consideration (ie, $C_x = m_x$) - the cost of setting up a method is a one time cost, and to an adversary with unlimited resources, expending a one time cost averages to $0$ over the long run. We will now explore the marginal cost of $x$. Censorship tools may slow down "good" traffic, and they may erroneously block access to good services. Therefore, $C_x = s_x*i_x + (u_{x,1}*c_{x,1} + u_{x,2}*c_{x,2} + ...  + u_{x,n}*c_{x,n})$, where $c_{x,n}$ is the average cost of blocking service $n$ per user, $u_{x,n}$ is the same as above, $s_x$ is the average fraction of the total value of unblocked traffic retained (due to the reduction in speed caused by enabling method $x$),\footnote{Note that an adversary may engage in multiple stages of filtering, so some subsets of unblocked traffic may experience no slowdown, while some might experience more. For the purposes of our analysis, we can use the average across all allowed traffic.}, and $i_x$ is the value per user of access to all unblocked sites. Combining the above, we see
$(u_{x,1}*b_{x,1} + u_{x,1}*b_{x,2} + ... + u_{x,n}*b_{x,n}) - s_x*i_x + (c_{x,1} + c_{x,2} + ...  + c_{x,n}) > 0$, or, more sucintly:
\begin{equation}

\end{equation}

We could conclude here if a censor engaged in censorship using
